---
title: "Clinician Screening Completion Tracker"
format: dashboard
scrolling: true 
---

<!-- ## Background and Purpose  -->
<!-- - We don’t have access to the EPIC EMR.  -->
<!-- - Providers will likely not be compliant with completing the research survey since it involves an extra step of doing this on REDcap, a system not integrated with their EMR.  -->
<!-- - We need a system to check compliance so that we can take appropriate actions in a timely manner.  -->
<!-- - We will run a dashboard report intermittently summarizing data measuring compliance pulled from REDcap.  -->
<!-- - The purpose of the code in this file is to create such a  report. -->

```{r, include = FALSE}
# Libraries
library(plotly)
library(here)
library(dplyr)
library(ggplot2)
library(flextable)
library(officer)
library(forcats, include.only = c("fct_reorder"))
```

```{r, include = FALSE}
# Load data
data_path <- here::here("data", "clinician_tracker_mock_data_calc.rds")
data <- readRDS(data_path)

# Load functions
source(here::here("r", "color_alert.R"))
source(here::here("r", "format_table.R"))
source(here::here("r", "time_series.R"))
```

#  {.sidebar}

<!-- Create Sidebar -->

```{r, echo=FALSE}
head_1 <- "This dashboard displays statistics for:\n\n"

data.frame(
  names = c("File Name", "Last Modified"),
  values = c(basename(data_path), format(Sys.time(), "%Y-%m-%d %H:%M %Z"))
) %>% flextable() %>%
  delete_part(part = "header") %>%
  bold(j = 1, part = "body") %>%
  border_remove() %>%
  width(j = c(1,2), width=c(1.2, 1.3), unit = "in") %>%
  add_header_lines(head_1) %>%
  color(j = c(1,2), color = "#6c757d", part = "body") %>%
  color(i = c(1), color = "#6c757d", part = "header") %>%
  bg(bg = "#ffffff", part = "body") %>%
  hline(part = "body", border = fp_border(color = "#f3f3f3")) %>%
  height_all(height= 0.5, unit = "in") %>%
  hrule(rule = "exact")

```

```{r, echo=FALSE}
subjects <- data %>% select(mrn) %>% unique() %>% nrow()
clinicians <- data %>% select(name_full_phys) %>% unique() %>% nrow()
appointments <- data %>% nrow()
time_period <- paste(min(as.Date(data$visit_date)), "to", max(as.Date(data$visit_date)))

head_2 <- "This data references:\n\n"

data.frame(
  names = c("Subjects", "Clinicians", "Appointments", "Time Period"),
  values = c(subjects, clinicians, appointments, time_period)
) %>% flextable() %>%
  delete_part(part = "header") %>%
  bold(j = 1, part = "body") %>%
  border_remove() %>%
  width(j = c(1,2), width=c(1.2, 1.2), unit = "in") %>%
  add_header_lines(head_2) %>%
  color(j = c(1,2), color = "#6c757d", part = "body") %>%
  color(i = c(1), color = "#6c757d", part = "header") %>%
  bg(bg = "#ffffff", part = "body") %>%
  hline(part = "body", border = fp_border(color = "#f3f3f3")) %>%
  height_all(height= 0.5, unit = "in") %>%
  hrule(rule = "exact")

```

# All

## Row {height= "25%" .fill}

```{r}
#| echo: false
#| title: Eligible Screened this Week
#| content: valuebox

# Filter this weeks data based on system time
today <- as.Date(Sys.time())

week <- data %>% 
  filter(as.Date(visit_date) %in% seq(today - 6, today, "day"))

perc_screened_week <- (sum(week$screened, na.rm = TRUE)/sum(week$eligible, na.rm = TRUE))*100

# Create value box  
list(
  icon = "check2-circle",
  color = color_code(perc_screened_week, 100),
  value = paste0(format(round(perc_screened_week, digits = 2),nsmall=2), "%"
                 )
)
```

```{r}
#| echo: false
#| title: Items Answered this Week 
#| content: valuebox

# Average proportion of items answered this week
items_answered_week <- mean(week$perc_completed, na.rm = TRUE)
  
# Create value box 
list(
  icon = "card-checklist",
  color = color_code(items_answered_week, 100),
  value = paste0(format(round(items_answered_week, digits = 2),nsmall=2), "%"
                 )
)
```

```{r}
#| echo: false
#| title: Items Answered Overall
#| content: valuebox

# Proportion of eligible screened
perc_completed <- mean(data$perc_completed, na.rm = TRUE)

# Create value box 
list(
  icon = "card-checklist",
  color = color_code(perc_completed, 100),
  value = paste0(format(round(perc_completed, digits = 2),nsmall=2), "%"
                 )
)
```

```{r}
#| echo: false
#| title: Eligible Screened Overall
#| content: valuebox

# Proportion of eligible screened
perc_screened <- (sum(data$screened, na.rm = TRUE)/sum(data$eligible, na.rm = TRUE))*100 

# Create value box 
list(
  icon = "check2-circle",
  color = color_code(perc_screened, 100),
  value = paste0(format(round(perc_screened, digits = 2),nsmall=2), "%"
                 )
)
```
## Row

### Column {width="30%"}

<!-- Overall counts data -->

```{r, include=FALSE}
overall_stats <- data.frame(
  name = c("Eligible Patient Appointments", "Screenings", 
           "Average Number of Items Answered"),
  value = c(sum(data["eligible"], na.rm = TRUE), 
            sum(data["screened"], na.rm = TRUE), 
            format(round(mean(data$num_completed, na.rm = TRUE), digits = 2), nsmall=2))
) 

```

<!-- This week's counts data -->

```{r, include=FALSE}
week_stats <- data.frame(
  name = c("Eligible Patient Appointments", "Screenings", 
           "Average Number of Items Answered"),
  value = c(sum(week["eligible"], na.rm = TRUE), 
            sum(week["screened"], na.rm = TRUE), 
            format(round(mean(week$num_completed, na.rm = TRUE), digits = 2), nsmall=2))
) 
```

#### Row

<!-- Create this week's counts table -->

```{r, echo=FALSE}
table_format(week_stats, "\nThis Week\n\n") 
```

#### Row

<!-- Create overall counts table -->

```{r}
table_format(overall_stats, "\nOverall\n\n")
```


### Column {.tabset}

```{r, echo=FALSE}
#| title: Proportion Screened
ht_text <- paste("<br>Clinic: %{text}",
  "<br>% of eligible patient appointments with screenings: %{y}%", 
  "<br>Month: %{x} <extra></extra>")

y_title <- "Percentage of Eligible Patient Appointments with Screenings"


data %>% 
  # Select relevant columns and filter for unique rows
  select(c(visit_date, month_year, clinic_name, perc_screened_month_clinic)) %>% 
  unique() %>%

# Plot data
time_series(.,"perc_screened_month_clinic", "clinic_name", ht_text, y_title)
```


```{r, echo=FALSE}
#| title: Proportion of Items Completed
ht_text <- paste("<br>Clinic: %{text}",
 " <br>% of survey items completed: %{y}%",
 "<br>Month: %{x} <extra></extra>")

y_title <- "Percentage of Survey Items Completed"


data %>% 
  # Select relevant columns and filter for unique rows
  select(c(visit_date, month_year, clinic_name, perc_items_month_clinic)) %>% 
  unique() %>%

# Plot data
time_series(.,"perc_items_month_clinic", "clinic_name", ht_text, y_title)
```

# Baylor

```{r}
baylor <- data %>% filter(clinic_name == "Baylor")
```


## Row {height="25%" .fill}

```{r}
#| echo: false
#| title: Eligible Screened this Week
#| content: valuebox

# Filter this week's data based on system date
today <- as.Date(Sys.time())

baylor_week <- baylor %>% 
  filter(as.Date(visit_date) %in% seq(today - 6, today, "day"))

# Proportion of eligible screened
perc_screened_week <- (sum(baylor_week$screened, na.rm = TRUE)/
                         sum(baylor_week$eligible, na.rm = TRUE))*100
  
# Create value box
list(
  icon = "check2-circle",
  color = color_code(perc_screened_week, 100),
  value = paste0(format(round(perc_screened_week, digits = 2),nsmall=2), "%"
                 )
)
```

```{r}
#| echo: false
#| title: Items Answered this Week 
#| content: valuebox

# Average proportion of items answered
items_answered_week <- mean(baylor_week$perc_completed, na.rm = TRUE)
  
# Create value box
list(
  icon = "card-checklist",
  color = color_code(items_answered_week, 100),
  value = paste0(format(round(items_answered_week, digits = 2),nsmall=2), "%"
                 )
)
```

```{r}
#| echo: false
#| title: Items Answered Overall
#| content: valuebox

# Proportion of eligible screened
perc_completed <- mean(baylor$perc_completed, na.rm = TRUE)

# Create value box
list(
  icon = "card-checklist",
  color = color_code(perc_completed, 100),
  value = paste0(format(round(perc_completed, digits = 2),nsmall=2), "%"
                 )
)
```

```{r}
#| echo: false
#| title: Eligible Screened Overall
#| content: valuebox

# Proportion of eligible screened
perc_screened <- (sum(baylor$screened, na.rm = TRUE)/
                    sum(baylor$eligible, na.rm = TRUE))*100 

# Create value box
list(
  icon = "check2-circle",
  color = color_code(perc_screened, 100),
  value = paste0(format(round(perc_screened, digits = 2),nsmall=2), "%"
                 )
)
```

## Row

<!-- Overall counts data -->

```{r, include=FALSE}
baylor_overall_stats <- data.frame(
  name = c("Eligible Patient Appointments", "Screenings", 
           "Average Number of Items Answered"),
  value = c(sum(baylor["eligible"], na.rm = TRUE), 
            sum(baylor["screened"], na.rm = TRUE), 
            format(round(
              mean(baylor$num_completed, na.rm = TRUE),
              digits = 2), nsmall=2))
) 
```

<!-- This week's counts data -->

```{r, include=FALSE}
baylor_week_stats <- data.frame(
  name = c("Eligible Patient Appointments", 
           "Screenings", "Average Number of Items Answered"),
  value = c(sum(baylor_week["eligible"], na.rm = TRUE), 
            sum(baylor_week["screened"], na.rm = TRUE), 
            format(round(
              mean(baylor_week$num_completed, na.rm = TRUE), 
              digits = 2), nsmall=2))
) 
```

### Column {width="30%"}

#### Row

<!-- Create this week's counts table -->

```{r, echo=FALSE}
table_format(baylor_week_stats, "\nThis Week\n\n") 
```

#### Row

<!-- Create overall counts table -->

```{r}
table_format(baylor_overall_stats, "\nOverall\n\n")
```


### Column {.tabset}

```{r, echo=FALSE}
#| title: Proportion Screened

ht_text <- paste("<br>Physician: %{text}",
          "<br>% of eligible patient appointments with screenings: %{y}%", 
          "<br>Month: %{x} <extra></extra>")

y_title <- "Percentage of Eligible Patient Appointments with Screenings"


# Select relevant columns and filter for unique rows
baylor %>% 
  select(c(visit_date, month_year, name_full_phys, perc_screened_month_phys))%>% 
  unique() %>%

# Plot data
time_series(.,"perc_screened_month_phys", "name_full_phys", ht_text, y_title)
```


```{r, echo=FALSE}
#| title: Proportion of Items Completed
ht_text <- paste("<br>Clinic: %{text}", 
          "<br>% of survey items completed: %{y}%", 
          "<br>Month: %{x} <extra></extra>")

y_title <- "Percentage of Survey Items Completed"


# Select relevant columns and filter for unique rows
baylor %>% 
  select(c(visit_date, month_year, name_full_phys, perc_items_month_phys))%>% 
  unique() %>%

# Plot data
time_series(.,"perc_items_month_phys", "name_full_phys", ht_text, y_title)
```

# Johns Hopkins

```{r}
jhop <- data %>% filter(clinic_name == "Johns Hopkins")
```


## Row {height="25%" .fill}

```{r}
#| echo: false
#| title: Eligible Screened this Week
#| content: valuebox

# Select relevant columns and filter for unique rows
today <- as.Date(Sys.time())

# Filter this week's data based on system time
jhop_week <- jhop %>% 
  filter(as.Date(visit_date) %in% seq(today - 6, today, "day"))

# Proportion of eligible screened
perc_screened_week <- (sum(jhop_week$screened, na.rm = TRUE)/
                         sum(jhop_week$eligible, na.rm = TRUE))*100
  
# Create value box
list(
  icon = "check2-circle",
  color = color_code(perc_screened_week, 100),
  value = paste0(format(round(perc_screened_week, digits = 2), nsmall=2), "%"
                 )
)
```

```{r}
#| echo: false
#| title: Items Answered this Week 
#| content: valuebox

# Average proportion of items answered this week
items_answered_week <- mean(jhop_week$perc_completed, na.rm = TRUE)
  
# Create value box
list(
  icon = "card-checklist",
  color = color_code(items_answered_week, 100),
  value = paste0(format(round(items_answered_week, digits = 2), nsmall=2), "%"
                 )
)
```

```{r}
#| echo: false
#| title: Items Answered Overall
#| content: valuebox

# Proportion of eligible screened
perc_completed <- mean(jhop$perc_completed, na.rm = TRUE)

# Create value box
list(
  icon = "card-checklist",
  color = color_code(perc_completed, 100),
  value = paste0(format(round(perc_completed, digits = 2),nsmall=2), "%"
                 )
)
```

<!-- ## Percent screened Overall-->

```{r}
#| echo: false
#| title: Eligible Screened Overall
#| content: valuebox

# Proportion of eligible screened
perc_screened <- (sum(jhop$screened, na.rm = TRUE)/
                    sum(jhop$eligible, na.rm = TRUE))*100 

# Create value box
list(
  icon = "check2-circle",
  color = color_code(perc_screened, 100),
  value = paste0(format(round(perc_screened, digits = 2),nsmall=2), "%"
                 )
)
```

## Row

<!-- Overall counts data -->

```{r, include=FALSE}
jhop_overall_stats <- data.frame(
  name = c("Eligible Patient Appointments", "Screenings", 
           "Average Number of Items Answered"),
  value = c(sum(jhop["eligible"], na.rm = TRUE), 
            sum(jhop["screened"], na.rm = TRUE), 
            format(round(
              mean(jhop$num_completed, na.rm = TRUE),
              digits = 2), nsmall=2))
) 
```

<!-- This week's counts data -->

```{r, include=FALSE}
jhop_week_stats <- data.frame(
  name = c("Eligible Patient Appointments", "Screenings", 
           "Average Number of Items Answered"),
  value = c(sum(jhop_week["eligible"], na.rm = TRUE), 
            sum(jhop_week["screened"], na.rm = TRUE), 
            format(round(
              mean(jhop_week$num_completed, na.rm = TRUE),
              digits = 2), nsmall=2))
) 
```

### Column {width="30%"}

#### Row

<!-- Create this week's counts table -->

```{r, echo=FALSE}
table_format(jhop_week_stats, "\nThis Week\n\n") 
```

#### Row

<!-- Create overall counts table -->

```{r}
table_format(jhop_overall_stats, "\nOverall\n\n")
```


### Column {.tabset}

```{r, echo=FALSE}
#| title: Proportion Screened
ht_text <- paste("<br>Physician: %{text}",
          "<br>% of eligible patient appointments with screenings: %{y}%", 
          "<br>Month: %{x} <extra></extra>")

y_title <- "Percentage of Eligible Patient Appointments with Screenings"


# Select relevant columns and filter for unique rows
jhop %>% 
  select(c(visit_date, month_year, name_full_phys, perc_screened_month_phys))%>% 
  unique() %>%

# Plot data
time_series(.,"perc_screened_month_phys", "name_full_phys", ht_text, y_title)
```


```{r, echo=FALSE}
#| title: Proportion of Items Completed
ht_text <- paste("<br>Clinic: %{text}", 
          "<br>% of survey items completed: %{y}%", 
          "<br>Month: %{x} <extra></extra>")

y_title <- "Percentage of Survey Items Completed"


# Select relevant columns and filter for unique rows
jhop %>% 
  # Select relevant columns and filter for unique rows
  select(c(visit_date, month_year, name_full_phys, perc_items_month_phys)) %>% 
  unique() %>%

# Plot data
time_series(.,"perc_items_month_phys", "name_full_phys", ht_text, y_title)
```

# LBJ

```{r}
lbj <- data %>% filter(clinic_name == "LBJ")
```


## Row {height="25%" .fill}

```{r}
#| echo: false
#| title: Eligible Screened this Week
#| content: valuebox

# Proportion of eligible screened
today <- as.Date(Sys.time())

lbj_week <- lbj %>% 
  filter(as.Date(visit_date) %in% seq(today - 6, today, "day"))

perc_screened_week <- (sum(lbj_week$screened, na.rm = TRUE)/
                         sum(lbj_week$eligible, na.rm = TRUE))*100
  

list(
  icon = "check2-circle",
  color = color_code(perc_screened_week, 100),
  value = paste0(format(round(perc_screened_week, digits = 2),nsmall=2), "%"
                 )
)
```

```{r}
#| echo: false
#| title: Items Answered this Week 
#| content: valuebox

items_answered_week <- mean(lbj_week$perc_completed, na.rm = TRUE)
  

list(
  icon = "card-checklist",
  color = color_code(items_answered_week, 100),
  value = paste0(format(round(items_answered_week, digits = 2),nsmall=2), "%"
                 )
)
```
<!-- ## Items Answered Overall-->

```{r}
#| echo: false
#| title: Items Answered Overall
#| content: valuebox

# Proportion of eligible screened
perc_completed <- mean(lbj$perc_completed, na.rm = TRUE)

list(
  icon = "card-checklist",
  color = color_code(perc_completed, 100),
  value = paste0(format(round(perc_completed, digits = 2),nsmall=2), "%"
                 )
)
```

<!-- ## Percent screened Overall-->

```{r}
#| echo: false
#| title: Eligible Screened Overall
#| content: valuebox

# Proportion of eligible screened
perc_screened <- (sum(lbj$screened, na.rm = TRUE)/
                    sum(lbj$eligible, na.rm = TRUE))*100 

list(
  icon = "check2-circle",
  color = color_code(perc_screened, 100),
  value = paste0(format(round(perc_screened, digits = 2), nsmall=2), "%"
                 )
)
```

## Row

```{r, include=FALSE}
lbj_overall_stats <- data.frame(
  name = c("Eligible Patient Appointments", "Screenings", 
           "Average Number of Items Answered"),
  value = c(sum(lbj["eligible"], na.rm = TRUE), 
            sum(lbj["screened"], na.rm = TRUE), 
            format(round(
              mean(lbj$num_completed, na.rm = TRUE), 
              digits = 2), nsmall=2))
) 

```

```{r, include=FALSE}
lbj_week_stats <- data.frame(
  name = c("Eligible Patient Appointments", "Screenings", 
           "Average Number of Items Answered"),
  value = c(sum(lbj_week["eligible"], na.rm = TRUE), 
            sum(lbj_week["screened"], na.rm = TRUE), 
            format(round(mean(lbj_week$num_completed, na.rm = TRUE), 
                         digits = 2), nsmall=2))
) 
```

### Column {width="30%"}

#### Row

```{r, echo=FALSE}
table_format(lbj_week_stats, "\nThis Week\n\n") 
```

#### Row

```{r}
table_format(lbj_overall_stats, "\nOverall\n\n")
```


### Column {.tabset}

```{r, echo=FALSE}
#| title: Proportion Screened
ht_text <- paste("<br>Physician: %{text}",
          "<br>% of eligible patient appointments with screenings: %{y}%", 
          "<br>Month: %{x} <extra></extra>")

y_title <- "Percentage of Eligible Patient Appointments with Screenings"


# Select relevant columns and filter for unique rows
lbj %>% 
  select(c(visit_date, month_year, name_full_phys, perc_screened_month_phys))%>% 
  unique() %>%

# Plot data
time_series(.,"perc_screened_month_phys", "name_full_phys", ht_text, y_title)
```


```{r, echo=FALSE}
#| title: Proportion of Items Completed
ht_text <- paste("<br>Clinic: %{text}", 
          "<br>% of survey items completed: %{y}%", 
          "<br>Month: %{x} <extra></extra>")

y_title <- "Percentage of Survey Items Completed"


# Select relevant columns and filter for unique rows
lbj %>% 
  # Select relevant columns and filter for unique rows
  select(c(visit_date, month_year, name_full_phys, perc_items_month_phys)) %>% 
  unique() %>%

# Plot data
time_series(.,"perc_items_month_phys", "name_full_phys", ht_text, y_title)
```


# UAB

```{r}
uab <- data %>% filter(clinic_name == "UAB")
```


## Row {height="25%" .fill}

```{r}
#| echo: false
#| title: Eligible Screened this Week
#| content: valuebox

# Proportion of eligible screened
today <- as.Date(Sys.time())

uab_week <- uab %>% 
  filter(as.Date(visit_date) %in% seq(today - 6, today, "day"))

perc_screened_week <- (sum(uab_week$screened, na.rm = TRUE)/
                         sum(uab_week$eligible, na.rm = TRUE))*100


list(
  icon = "check2-circle",
  color = color_code(perc_screened_week, 100),
  value = paste0(format(round(perc_screened_week, digits = 2),nsmall=2), "%"
  )
)
```

```{r}
#| echo: false
#| title: Items Answered this Week 
#| content: valuebox

items_answered_week <- mean(uab_week$perc_completed, na.rm = TRUE)


list(
  icon = "card-checklist",
  color = color_code(items_answered_week, 100),
  value = paste0(format(round(items_answered_week, digits = 2),nsmall=2), "%"
  )
)
```
<!-- ## Items Answered Overall-->
  
```{r}
#| echo: false
#| title: Items Answered Overall
#| content: valuebox

# Proportion of eligible screened
perc_completed <- mean(uab$perc_completed, na.rm = TRUE)

list(
  icon = "card-checklist",
  color = color_code(perc_completed, 100),
  value = paste0(format(round(perc_completed, digits = 2),nsmall=2), "%"
  )
)
```

<!-- ## Percent screened Overall-->
  
```{r}
#| echo: false
#| title: Eligible Screened Overall
#| content: valuebox

# Proportion of eligible screened
perc_screened <- (sum(uab$screened, na.rm = TRUE)/
                    sum(uab$eligible, na.rm = TRUE))*100 

list(
  icon = "check2-circle",
  color = color_code(perc_screened, 100),
  value = paste0(format(round(perc_screened, digits = 2), nsmall=2), "%"
  )
)
```

## Row

```{r, include=FALSE}
uab_overall_stats <- data.frame(
  name = c("Eligible Patient Appointments", "Screenings", 
           "Average Number of Items Answered"),
  value = c(sum(uab["eligible"], na.rm = TRUE), 
            sum(uab["screened"], na.rm = TRUE), 
            format(round(
              mean(uab$num_completed, na.rm = TRUE),
              digits = 2), nsmall=2))
) 

```

```{r, include=FALSE}
uab_week_stats <- data.frame(
  name = c("Eligible Patient Appointments", "Screenings", 
           "Average Number of Items Answered"),
  value = c(sum(uab_week["eligible"], na.rm = TRUE), 
            sum(uab_week["screened"], na.rm = TRUE), 
            format(round(
              mean(uab_week$num_completed, na.rm = TRUE), 
              digits = 2), nsmall=2))
) 
```

### Column {width="30%"}

#### Row

```{r, echo=FALSE}
table_format(uab_week_stats, "\nThis Week\n\n") 
```

#### Row

```{r}
table_format(uab_overall_stats, "\nOverall\n\n")
```


### Column {.tabset}

```{r, echo=FALSE}
#| title: Proportion Screened
ht_text <- paste("<br>Physician: %{text}",
          "<br>% of eligible patient appointments with screenings: %{y}%", 
          "<br>Month: %{x} <extra></extra>")

y_title <- "Percentage of Eligible Patient Appointments with Screenings"


# Select relevant columns and filter for unique rows
uab %>% 
  select(c(visit_date, month_year, name_full_phys, perc_screened_month_phys))%>% 
  unique() %>%

# Plot data
time_series(.,"perc_screened_month_phys", "name_full_phys", ht_text, y_title)
```


```{r, echo=FALSE}
#| title: Proportion of Items Completed
ht_text <- paste("<br>Clinic: %{text}", 
          "<br>% of survey items completed: %{y}%", 
          "<br>Month: %{x} <extra></extra>")

y_title <- "Percentage of Survey Items Completed"


# Select relevant columns and filter for unique rows
uab %>% 
  # Select relevant columns and filter for unique rows
  select(c(visit_date, month_year, name_full_phys, perc_items_month_phys)) %>% 
  unique() %>%

# Plot data
time_series(.,"perc_items_month_phys", "name_full_phys", ht_text, y_title)
```


# UCSF

```{r}
ucsf <- data %>% filter(clinic_name == "UCSF")
```


## Row {height="25%" .fill}

```{r}
#| echo: false
#| title: Eligible Screened this Week
#| content: valuebox

# Proportion of eligible screened
today <- as.Date(Sys.time())

ucsf_week <- ucsf %>% 
  filter(as.Date(visit_date) %in% seq(today - 6, today, "day"))

perc_screened_week <- (sum(ucsf_week$screened, na.rm = TRUE)/
                         sum(ucsf_week$eligible, na.rm = TRUE))*100


list(
  icon = "check2-circle",
  color = color_code(perc_screened_week, 100),
  value = paste0(format(round(perc_screened_week, digits = 2),nsmall=2), "%"
  )
)
```

```{r}
#| echo: false
#| title: Items Answered this Week 
#| content: valuebox

items_answered_week <- mean(ucsf_week$perc_completed, na.rm = TRUE)


list(
  icon = "card-checklist",
  color = color_code(items_answered_week, 100),
  value = paste0(format(round(items_answered_week, digits = 2),nsmall=2), "%"
  )
)
```
<!-- ## Items Answered Overall-->
  
```{r}
#| echo: false
#| title: Items Answered Overall
#| content: valuebox

# Proportion of eligible screened
perc_completed <- mean(ucsf$perc_completed, na.rm = TRUE)

list(
  icon = "card-checklist",
  color = color_code(perc_completed, 100),
  value = paste0(format(round(perc_completed, digits = 2),nsmall=2), "%"
  )
)
```

<!-- ## Percent screened Overall-->
  
```{r}
#| echo: false
#| title: Eligible Screened Overall
#| content: valuebox

# Proportion of eligible screened
perc_screened <- (sum(ucsf$screened, na.rm = TRUE)/
                    sum(ucsf$eligible, na.rm = TRUE))*100 

list(
  icon = "check2-circle",
  color = color_code(perc_screened, 100),
  value = paste0(format(round(perc_screened, digits = 2), nsmall=2), "%"
  )
)
```

## Row

```{r, include=FALSE}
ucsf_overall_stats <- data.frame(
  name = c("Eligible Patient Appointments", "Screenings", 
           "Average Number of Items Answered"),
  value = c(sum(ucsf["eligible"], na.rm = TRUE), 
            sum(ucsf["screened"], na.rm = TRUE), 
            format(round(
              mean(ucsf$num_completed, na.rm = TRUE), 
              digits = 2), nsmall=2))
) 

```

```{r, include=FALSE}
ucsf_week_stats <- data.frame(
  name = c("Eligible Patient Appointments", "Screenings", 
           "Average Number of Items Answered"),
  value = c(sum(ucsf_week["eligible"], na.rm = TRUE), 
            sum(ucsf_week["screened"], na.rm = TRUE), 
            format(round(
              mean(ucsf_week$num_completed, na.rm = TRUE), 
              digits = 2), nsmall=2))
) 
```

### Column {width="30%"}

#### Row

```{r, echo=FALSE}
table_format(ucsf_week_stats, "\nThis Week\n\n") 
```

#### Row

```{r}
table_format(ucsf_overall_stats, "\nOverall\n\n")
```


### Column {.tabset}

```{r, echo=FALSE}
#| title: Proportion Screened
ht_text <- paste("<br>Physician: %{text}",
          "<br>% of eligible patient appointments with screenings: %{y}%", 
          "<br>Month: %{x} <extra></extra>")

y_title <- "Percentage of Eligible Patient Appointments with Screenings"


# Select relevant columns and filter for unique rows
ucsf %>% 
  select(c(visit_date, month_year, name_full_phys, perc_screened_month_phys))%>% 
  unique() %>%

# Plot data
time_series(.,"perc_screened_month_phys", "name_full_phys", ht_text, y_title)
```


```{r, echo=FALSE}
#| title: Proportion of Items Completed
ht_text <- paste("<br>Clinic: %{text}", 
          "<br>% of survey items completed: %{y}%", 
          "<br>Month: %{x} <extra></extra>")

y_title <- "Percentage of Survey Items Completed"


# Select relevant columns and filter for unique rows
ucsf %>% 
  # Select relevant columns and filter for unique rows
  select(c(visit_date, month_year, name_full_phys, perc_items_month_phys)) %>% 
  unique() %>%

# Plot data
time_series(.,"perc_items_month_phys", "name_full_phys", ht_text, y_title)
```

# UT Physicians

```{r}
ut_phys <- data %>% filter(clinic_name == "UT Physicians")
```


## Row {height="25%" .fill}

```{r}
#| echo: false
#| title: Eligible Screened this Week
#| content: valuebox

# Proportion of eligible screened
today <- as.Date(Sys.time())

ut_phys_week <- ut_phys %>% 
  filter(as.Date(visit_date) %in% seq(today - 6, today, "day"))

perc_screened_week <- (sum(ut_phys_week$screened, na.rm = TRUE)/
                         sum(ut_phys_week$eligible, na.rm = TRUE))*100


list(
  icon = "check2-circle",
  color = color_code(perc_screened_week, 100),
  value = paste0(format(round(perc_screened_week, digits = 2),nsmall=2), "%"
  )
)
```

```{r}
#| echo: false
#| title: Items Answered this Week 
#| content: valuebox

items_answered_week <- mean(ut_phys_week$perc_completed, na.rm = TRUE)


list(
  icon = "card-checklist",
  color = color_code(items_answered_week, 100),
  value = paste0(format(round(items_answered_week, digits = 2),nsmall=2), "%"
  )
)
```
<!-- ## Items Answered Overall-->
  
```{r}
#| echo: false
#| title: Items Answered Overall
#| content: valuebox

# Proportion of eligible screened
perc_completed <- mean(ut_phys$perc_completed, na.rm = TRUE)

list(
  icon = "card-checklist",
  color = color_code(perc_completed, 100),
  value = paste0(format(round(perc_completed, digits = 2),nsmall=2), "%"
  )
)
```

<!-- ## Percent screened Overall-->
  
```{r}
#| echo: false
#| title: Eligible Screened Overall
#| content: valuebox

# Proportion of eligible screened
perc_screened <- (sum(ut_phys$screened, na.rm = TRUE)/
                    sum(ut_phys$eligible, na.rm = TRUE))*100 

list(
  icon = "check2-circle",
  color = color_code(perc_screened, 100),
  value = paste0(format(round(perc_screened, digits = 2),nsmall=2), "%"
  )
)
```

## Row

```{r, include=FALSE}
ut_phys_overall_stats <- data.frame(
  name = c("Eligible Patient Appointments", "Screenings", 
           "Average Number of Items Answered"),
  value = c(sum(ut_phys["eligible"], na.rm = TRUE), 
            sum(ut_phys["screened"], na.rm = TRUE), 
            format(round(mean(ut_phys$num_completed, na.rm = TRUE)
                         , digits = 2), nsmall=2))
) 

```

```{r, include=FALSE}
ut_phys_week_stats <- data.frame(
  name = c("Eligible Patient Appointments", "Screenings", 
           "Average Number of Items Answered"),
  value = c(sum(ut_phys_week["eligible"], na.rm = TRUE), 
            sum(ut_phys_week["screened"], na.rm = TRUE), 
            format(round(
              mean(ut_phys_week$num_completed, na.rm = TRUE), 
              digits = 2), nsmall=2))
) 
```

### Column {width="30%"}

#### Row

```{r, echo=FALSE}
table_format(ut_phys_week_stats, "\nThis Week\n\n") 
```

#### Row

```{r}
table_format(ut_phys_overall_stats, "\nOverall\n\n")
```


### Column {.tabset}

```{r, echo=FALSE}
#| title: Proportion Screened
ht_text <- paste("<br>Physician: %{text}",
          "<br>% of eligible patient appointments with screenings: %{y}%", 
          "<br>Month: %{x} <extra></extra>")

y_title <- "Percentage of Eligible Patient Appointments with Screenings"


# Select relevant columns and filter for unique rows
ut_phys %>% 
  select(c(visit_date, month_year, name_full_phys, perc_screened_month_phys))%>% 
  unique() %>%

# Plot data
time_series(.,"perc_screened_month_phys", "name_full_phys", ht_text, y_title)
```


```{r, echo=FALSE}
#| title: Proportion of Items Completed
ht_text <- paste("<br>Clinic: %{text}", 
          "<br>% of survey items completed: %{y}%", 
          "<br>Month: %{x} <extra></extra>")

y_title <- "Percentage of Survey Items Completed"


# Select relevant columns and filter for unique rows
ut_phys %>% 
  # Select relevant columns and filter for unique rows
  select(c(visit_date, month_year, name_full_phys, perc_items_month_phys)) %>% 
  unique() %>%

# Plot data
time_series(.,"perc_items_month_phys", "name_full_phys", ht_text, y_title)
```

# UTSW

```{r}
utsw <- data %>% filter(clinic_name == "UTSW")
```


## Row {height="25%" .fill}

```{r}
#| echo: false
#| title: Eligible Screened this Week
#| content: valuebox

# Proportion of eligible screened
today <- as.Date(Sys.time())

utsw_week <- utsw %>% 
  filter(as.Date(visit_date) %in% seq(today - 6, today, "day"))

perc_screened_week <- (sum(utsw_week$screened, na.rm = TRUE)/
                         sum(utsw_week$eligible, na.rm = TRUE))*100


list(
  icon = "check2-circle",
  color = color_code(perc_screened_week, 100),
  value = paste0(format(round(perc_screened_week, digits = 2),nsmall=2), "%"
  )
)
```

```{r}
#| echo: false
#| title: Items Answered this Week 
#| content: valuebox

items_answered_week <- mean(utsw_week$perc_completed, na.rm = TRUE)


list(
  icon = "card-checklist",
  color = color_code(items_answered_week, 100),
  value = paste0(format(round(items_answered_week, digits = 2),nsmall=2), "%"
  )
)
```
<!-- ## Items Answered Overall-->
  
```{r}
#| echo: false
#| title: Items Answered Overall
#| content: valuebox

# Proportion of eligible screened
perc_completed <- mean(utsw$perc_completed, na.rm = TRUE)

list(
  icon = "card-checklist",
  color = color_code(perc_completed, 100),
  value = paste0(format(round(perc_completed, digits = 2),nsmall=2), "%"
  )
)
```

<!-- ## Percent screened Overall-->
  
```{r}
#| echo: false
#| title: Eligible Screened Overall
#| content: valuebox

# Proportion of eligible screened
perc_screened <- (sum(utsw$screened, na.rm = TRUE)/
                    sum(utsw$eligible, na.rm = TRUE))*100 

list(
  icon = "check2-circle",
  color = color_code(perc_screened, 100),
  value = paste0(format(round(perc_screened, digits = 2),nsmall=2), "%"
  )
)
```

## Row

```{r, include=FALSE}
utsw_overall_stats <- data.frame(
  name = c("Eligible Patient Appointments", "Screenings", 
           "Average Number of Items Answered"),
  value = c(sum(utsw["eligible"], na.rm = TRUE), 
            sum(utsw["screened"], na.rm = TRUE), 
            format(round(
              mean(utsw$num_completed, na.rm = TRUE),
              digits = 2), nsmall=2))
) 

```

```{r, include=FALSE}
utsw_week_stats <- data.frame(
  name = c("Eligible Patient Appointments", "Screenings", 
           "Average Number of Items Answered"),
  value = c(sum(utsw_week["eligible"], na.rm = TRUE), 
            sum(utsw_week["screened"], na.rm = TRUE), 
            format(round(
              mean(utsw_week$num_completed, na.rm = TRUE), 
              digits = 2), nsmall=2))
) 
```

### Column {width="30%"}

#### Row

```{r, echo=FALSE}
table_format(utsw_week_stats, "\nThis Week\n\n") 
```

#### Row

```{r}
table_format(utsw_overall_stats, "\nOverall\n\n")
```


### Column {.tabset}

```{r, echo=FALSE}
#| title: Proportion Screened
ht_text <- paste("<br>Physician: %{text}",
          "<br>% of eligible patient appointments with screenings: %{y}%", 
          "<br>Month: %{x} <extra></extra>")

y_title <- "Percentage of Eligible Patient Appointments with Screenings"


# Select relevant columns and filter for unique rows
utsw %>% 
  select(c(visit_date, month_year, name_full_phys, perc_screened_month_phys))%>% 
  unique() %>%

# Plot data
time_series(.,"perc_screened_month_phys", "name_full_phys", ht_text, y_title)
```


```{r, echo=FALSE}
#| title: Proportion of Items Completed
ht_text <- paste("<br>Clinic: %{text}", 
          "<br>% of survey items completed: %{y}%", 
          "<br>Month: %{x} <extra></extra>")

y_title <- "Percentage of Survey Items Completed"


# Select relevant columns and filter for unique rows
utsw %>% 
  # Select relevant columns and filter for unique rows
  select(c(visit_date, month_year, name_full_phys, perc_items_month_phys)) %>% 
  unique() %>%

# Plot data
time_series(.,"perc_items_month_phys", "name_full_phys", ht_text, y_title)
```
