---
title: "Clean DETECT tool pilot study data imported from REDCap"
---

# Overview

In this file, we do some initial cleaning of the DETECT tool pilot study data imported from REDCap to prepare it for dashbord summary. This pilot lasted for 2 weeks, starting on 11/11/2024 and ending on 11/25/2023.


# Load packages

```{r, message= FALSE}
library(dplyr, warn.conflicts = FALSE)
library(readr)
library(purrr)
library(stringr)
library(janitor)
library(here)
```


# Load custom functions

```{r}
source(here::here("R", "recoding_factoring_relocating.R"))
source(here::here("R", "nums_to_na.R"))
source(here::here("R", "data_cleaning_tools.R"))
```


# Load data

```{r}
tool_pilot <- read_csv(here::here("data", "detect_tool_pilot_test_raw.csv"))
tool_pilot_labels <- read_csv(
  here::here("data", "detect_tool_pilot_test_labels_raw.csv"))
link_hits <- read_csv(here::here("data", "detect_tool_pilot_link_hits.csv"))
```


# Data cleaning

Here we will convert all variable names to snake case with double underscores reduced to single underscores so that everything is uniform.

```{r}
tool_pilot <- clean_names(tool_pilot)
```


# Filter only data for dates relevant to the pilot

```{r}
# Create sequence of relevant dates
dates <- c(seq(as.Date('2024-11-11'), as.Date('2024-11-25'), by = "day"))

# Filter the reporting_instrument_timestamp variable to include only dates in
# sequence
tool_pilot <- tool_pilot %>% filter(as.Date(reporting_instrument_timestamp) %in% dates)
```


# Create a dataframe with variable descriptions

Extract the column names from the data and labels data frames to create a data frame of variable descriptions.

```{r}
labels <- c("Record ID", "Survey Identifier", "Survey Timestamp", 
           "Form start timestamp", "Form date", "Enter survey password", 
           "Password verification", "Password verification", "Patient MRN", 
           "Institution", "Baylor clinician name", "Other Baylor clinician name", 
           "Johns Hopkins clinician name", "Other Johns Hopkins clinician name", 
           "UCSF clinician name", "Other UCSF clinician name", 
           "UAB clinician name", "Other UAB clinician name", 
           "UTSW clinician name", "Other UTSW clinician name", 
           "LBJ clinician name", "Other LBJ clinician name", 
           "UTP clinician name", "Other UTP clinician name", "Clinician ID", 
           "Clinician name", "Absence of necessities ", 
           "Health or safety concern", "Environment not assessed reason", 
           "Defensive", "Caregiver not assessed reason", 
           "Other reason caregiver not assessed", "Chemically sedated", 
           "Isolated", "Anxious", "Prohibited", "Unmet needs", 
           "Unexplained injuries", "Patient not assessed reason", 
           "Suspect EM", "Indicators observed but EM not suspected explanation", 
           "Suspect EM explanation", "Self-neglect suspected", 
           "Financial exploitation suspected", 
           "Emotional or psychological abuse suspected", 
           "Physical abuse suspected", "Sexual abuse suspected", 
           "Caregiver neglect suspected", "Abandonment suspected", 
           "Other mistreatment type suspected", 
           "Dont know/ Not sure of mistreatment type", 
           "Specified other mistreatment type suspected", 
           "Intention to report to APS", 
           "No intention to report to APS explanation", 
           "Other service referral", "Specify other service", "Story", 
           "Story note", "Complete"
)

var_desc <- data.frame(variable = names(tool_pilot),
                       description = names(tool_pilot_labels),
                       label = labels)

```


# Replace certain numerically coded variables with character values

```{r}
# Create a named vector with variable names and variable descriptions 
naming_vec <- setNames(as.list(var_desc$description),
                               var_desc$variable)
```

```{r}
# Order of variables
vars <- unlist(var_desc$variable)
```


```{r}
screening_items <- c("ri_necessities", "ri_environment", "ri_caregiver", 
                     "ri_sedated", "ri_isolated", "ri_anxious", "ri_prohibited", 
                     "ri_unmet_needs", "ri_injuries")

tool_pilot_labels <- tool_pilot_labels %>% rename(unlist(naming_vec)) %>% 
  select(record_id, ri_institution, ri_clinician_bcm, ri_clinician_jh, 
         ri_clinician_ucsf, ri_clinician_uab, ri_clinician_utsw, 
         ri_clinician_lbj, ri_clinician_utp, all_of(screening_items))

tool_pilot <- tool_pilot %>% select(-c(ri_institution, ri_clinician_bcm, ri_clinician_jh, 
         ri_clinician_ucsf, ri_clinician_uab, ri_clinician_utsw, 
         ri_clinician_lbj, ri_clinician_utp, all_of(screening_items))) %>% 
  left_join(tool_pilot_labels, by = "record_id") %>%
  # re-oder variables
  select(all_of(vars))
```

```{r}
link_hits <- link_hits %>% 
  tidyr::pivot_longer(!date, names_to = "link", values_to = "hits")
```


```{r}
write_rds(tool_pilot, here::here("data", "detect_tool_pilot.RDS"))
write_rds(var_desc, here::here("data", 
                               "detect_tool_pilot_variable_descriptions.RDS"))
write_rds(link_hits, here::here("data", 
                               "detect_tool_pilot_link_hits_long_format.RDS"))
```




